### 2018-02-14 doc/manuscript.Rmd
moved analysis of gee and pls into rda files

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "YearsFromBaseline")
gee_adj_df <- analyze_gee()
```

```{r analyze_others}
# CV results are shown in pls.Rmd vignette
pls_homa2 <- analyze_pls(y = 'lHOMA2_S', cv = FALSE)
pls_isi <- analyze_pls(y = 'lISI', cv = FALSE)

# Correlation between predicted and observed
pls_homa2_t <- analyze_pls(y = 'lHOMA2_S')
pls_isi_t <- analyze_pls(y = 'lISI')
pls_igi_t <- analyze_pls(y = 'lIGIIR')
pls_issi2_t <- analyze_pls(y = 'lISSI2')

cor_df <- analyze_corr()
cor_df_mol <- analyze_corr(y = tg_pct)
cor_df_tagfa <- analyze_corr_tagfa()

pls_gee <- project_data %>%
    analyze_gee(
        x = c('Comp1', 'Comp2'),
        data_prep = 'pls',
        pls_results = pls_isi
        ) %>% 
    dplyr::select(Yterms, Xterms, estimate, p.value) %>% 
    dplyr::filter(Xterms == 'Comp1') %>% 
    dplyr::mutate(p.value = format_p(p.value),
                  estimate = format_rounding(estimate))
```

>>>>

```{r analyze_others}
# Correlation between predicted and observed
pls_homa2_t <- analyze_pls(y = 'lHOMA2_S')
pls_isi_t <- analyze_pls(y = 'lISI')
pls_igi_t <- analyze_pls(y = 'lIGIIR')
pls_issi2_t <- analyze_pls(y = 'lISSI2')

pls_gee <- project_data %>%
    analyze_gee(
        x = c('Comp1', 'Comp2'),
        data_prep = 'pls',
        pls_results = pls_results$pls_isi_df
        ) %>% 
    dplyr::select(Yterms, Xterms, estimate, p.value) %>% 
    dplyr::filter(Xterms == 'Comp1') %>% 
    dplyr::mutate(p.value = aide::format_pval(p.value),
                  estimate = aide::format_round(estimate))
```
